Large squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-07-12 large_number_squeezing_with_atoms.tex
Redo GD's fix which I screwed up
Finish re-applying my changes that Mattias accidentally backed-out.

We will work in the Heisenberg picture, and derive expressions for $\hat{a}(t_3)$ and $\hat{b}(t_3)$ in terms of $\hat{a}(t_2)$ and $\hat{b}(t_2)$, which in turn can be expressed in terms of $\hat{a}(t_1)$ and $\hat{b}(t_1)$. We will show that the state of the system at time $t_1$ consists of seperate coherent states in modes $|a\rangle$ and $|b\rangle$, enabling us to calculate expectation values at time $t_3$ in terms of the known state at $t_1$.

>>>>

We will work in the Heisenberg picture, and derive expressions for $\hat{a}(t_3)$ and $\hat{b}(t_3)$ in terms of $\hat{a}(t_2)$ and $\hat{b}(t_2)$, which in turn can be expressed in terms of $\hat{a}(t_1)$ and $\hat{b}(t_1)$. We will show that the state of the system at time $t_1$ consists of separate coherent states in modes $|a\rangle$ and $|b\rangle$, enabling us to calculate expectation values at time $t_3$ in terms of the known state at $t_1$.
